\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,graphicx,paralist,setspace,amsthm,pdflscape,fancyhdr,fullpage,rotating,tikz,xcolor,float,varwidth,eurosym}
%\usepackage{times}
\usepackage{longtable}
\usepackage{sectsty}
\usepackage[compact]{titlesec}
\sectionfont{\centering\large}
\subsectionfont{\centering\normalsize}
\usepackage{subfloat}
\usepackage{subcaption}
%\usepackage{harvard}
\usepackage[]{har2nat}
\setcitestyle{aysep={}}
\setcitestyle{notesep={, }}
%\citationstyle{dcu}\usepackage{appendix}
\usepackage[space]{grffile}
\bibliographystyle{apsr}
\newtheorem{hypot}{Hypothesis}
\usepackage[breaklinks,urlcolor=blue,citecolor=blue,linkcolor=blue,linktocpage=true,backref=true]{hyperref}
\usepackage{setspace} % load setspace before footmisc
\usepackage{footmisc}
\renewcommand{\footnotelayout}{\doublespacing}
\setlength{\footnotesep}{\baselineskip}
\hypersetup{
	colorlinks=true,
	urlcolor=blue
}

\newtheorem{hyp}{Hypothesis}
\makeatletter
\newcounter{subhyp} 
\let\savedc@hyp\c@hypd
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
} 


\usepackage[space]{grffile}
\graphicspath{{../}{../Figures/}}

\newcommand{\possessivecite}[1]{\citeauthor{#1}'s \citeyear{#1}}


\begin{document}

\title{Global Guardians: The U.S. Military and Minority Public Opinion in Host States\thanks{This material is based upon work supported by, or in part by, the U.S. Army Research Laboratory and the U.S. Army Research Office under grant number W911NF-18-1-0087.  Opinions and interpretations are those of the author and not the Army or Department of Defense. All authors contributed equally to this article and are thus listed in a rotating alphabetical ordering. All remaining errors are our own.}} %don't forget thank yous in a future version.
\author{Michael E. Flynn\thanks{\textbf{Email:} \href{mailto:meflynn@ksu.edu}{\tt meflynn@ksu.edu}. \textbf{Contact:} Department of Political Science, 019C Calvin Hall, Kansas State University, Manhattan, KS 66506.} \\
Department of Political Science \\
Kansas State University \\
\and Carla Martinez Machain\thanks{\textbf{Email:} \href{mailto:carlamm@ksu.edu}{\tt carlamm@ksu.edu}. \textbf{Contact:} Department of Political Science, 101C Calvin Hall, Kansas State University, Manhattan, KS 66506.}\\
Department of Political Science\\
Kansas State University \\
\and
Andrew Stravers\thanks{\textbf{Email:} \href{mailto:stravers@utexas.edu }{\tt stravers@utexas.edu }. \textbf{Contact:} The University of Texas at Austin, 158 W 21st ST STOP A1800, Batts Hall 2.116, Austin, TX 78712-1704.}\\
Department of Government\\
University of Texas--Austin \\
\and
Michael A. Allen\thanks{\textbf{Email:} \href{mailto:michaelaallen@boisestate.edu}{\tt michaelaallen@boisestate.edu}. \textbf{Contact:} Department of Political Science, Boise State University, 1910 University Drive, Boise, ID 83725.}\\
Department of Political Science\\
Boise State University
}



\maketitle
\thispagestyle{empty}



\clearpage

\begin{abstract}
The United States often portrays itself as an ally of minority groups abroad. Through its interventions in the Balkans, in different parts of Africa, and its support of the Kurds in Iraq, American military power has often been brought to bear to protect minority groups from hostile and repressive governments. However, the United States itself has also had problems with violating the rights of ethnic minorities within its own borders and has also been accused of exporting attitudes of racial inferiority, stereotypes, and hierarchies into foreign states. Do minority populations in states that host the US military see it as a friend or a foe? We argue that long term deployments in peaceful countries create direct and indirect paths toward minority discontent with the United States. Directly, Status of Forces Agreements between host states and the United States will place some of the basing burden on minority groups not well represented by host-state governments. Indirectly, the very act of basing sends credible signals about US commitment to the host state and empowers it to maintain status quo policies towards disenfranchised groups. These combined forces compel minority groups to see the United States in a less positive terms than the dominant group does. We test our hypotheses using original survey data from 14 different countries that host U.S. military forces. 
\end{abstract}



\vfill

\titlespacing{\section}{0pt}{*2}{*0}
\titlespacing{\subsection}{0pt}{*2}{*0}
\titlespacing{\subsubsection}{0pt}{1cm}{*0}

\thispagestyle{empty}


\newpage
\setcounter{page}{1}
\doublespacing
\input{introMinority}
\input{backgroundMinority}
\input{theoryMinority}
\input{rdMinority}
\input{resultsMinority}
\input{conclusionMinority}


\newpage

%\bibliographystyle{apsr01}
\bibliography{one}

%\newpage
%\input{appendixSpending}

\end{document}