
\section*{Acknowledgments}

This book was a large project that involved the help of many different friends and colleagues. We appreciate the feedback we received in several different venues that we have presented material from this project including the Latin American Peace Science (2018), Peace Science (2019), International Studies Association (2019-2021), International Studies Association Midwest (2018) American Political Science Association (2018-2021), University of Minnesota Humphrey School (2019), Bridging the Gap IPSI workshop (2019), University of Chicago WIPS lecture series and CPOST (2020), the Utah State University (2020), Army Strategic Futures Conference (2020), the Homeland Defense \& Security Information Analysis Center (2020), the Annual Minerva Meeting (2020),  and the Pacific Northwest Political Science Association (2020).

In particular, we appreciate detailed read through and feedback from Ryan Grauer, Sibel Oktay, Spencer Willardson, and Oliver Kaplan. In addition, several people provided valuable feedback at various critical points in this project including Sam Bell, Ben Farrer, Mike Findley, Adrian Florea, Benjamin Fordham, Benjamin Jones, Patrick McDonald, Steve Miller, Julie VanDusky-Allen, Rob Williams, Andrew Heiss, Jon POe, Vincent Arel-Bundock, Matt Blackwell, Bob Pape, Paul Poast, Paul Staniland, Austin Carson, Arlene Tickner, Sebastian Bitar, Mike Findley, Mark Nieman, Ric Stoll, and Cliff Morgan

We would like to thank our Graduate Research assistants for their valuable time and feedback. Nachelle Ronquillo, Sinan Nadarevic, Thomas Campbell, and... we thank you very much for your dedication.

Additionally, this project would not be possible without the funding of the Minerva Research Initiative. We would like to thank Lisa Troyer and David Montgomery for their assistance in making this research feasible in the first place. Likewise, thank you to our interview subjects and all 42,000 people who took our survey. Additionally, this material is based upon work supported by, or in part by, the Minerva Research Initiative, US Army Research Laboratory, and the US Army Research Office under grant number W911NF-18-1-0087. Opinions and interpretations are those of the author and not the US Army or Department of Defense but ours alone





