\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,graphicx,paralist,setspace,amsthm,pdflscape,fancyhdr,fullpage,rotating,tikz,xcolor,float,varwidth,eurosym}
%\usepackage{times}
\usepackage{longtable}
\usepackage{sectsty}
\usepackage[compact]{titlesec}
\sectionfont{\centering\large}
\subsectionfont{\centering\normalsize}
\usepackage{subfigure}
%\usepackage{harvard}
\usepackage[]{har2nat}
\setcitestyle{aysep={}}
\setcitestyle{notesep={, }}
%\citationstyle{dcu}\usepackage{appendix}
\usepackage[space]{grffile}
\bibliographystyle{apsr}
\newtheorem{hypot}{Hypothesis}
\usepackage[urlcolor=blue,citecolor=blue,linkcolor=blue,linktocpage=true,backref=true]{hyperref}
\usepackage{setspace} % load setspace before footmisc
\usepackage{footmisc}
\renewcommand{\footnotelayout}{\doublespacing}
\setlength{\footnotesep}{\baselineskip}
\hypersetup{
	colorlinks=true,
	urlcolor=blue
}

\newtheorem{hyp}{Hypothesis}
\makeatletter
\newcounter{subhyp} 
\let\savedc@hyp\c@hyp
\newenvironment{subhyp}
 {%
  \setcounter{subhyp}{0}%
  \stepcounter{hyp}%
  \edef\saved@hyp{\thehyp}% Save the current value of hyp
  \let\c@hyp\c@subhyp     % Now hyp is subhyp
  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
 }
 {}
\newcommand{\normhyp}{%
  \let\c@hyp\savedc@hyp % revert to the old one
  \renewcommand\thehyp{\arabic{hyp}}%
} 


\usepackage[space]{grffile}
\graphicspath{{./}{./Data/}{./Tables/}{./Figures/}}

\newcommand{\possessivecite}[1]{\citeauthor{#1}'s \citeyear{#1}}


\begin{document}

\title{The Good, Bad, and Ugly American: Explaining Variation in Global Anti-US Military Base Protests\footnote{} \thanks{This material is based upon work supported by, or in part by, the U.S. Army Research Laboratory and the U.S. Army Research Office under grant number W911NF-18-1-0087. The authors would like to thank xxx for their valuable help in preparing this manuscript. All remaining errors are our own.}}
\author{Carla Martinez Machain\thanks{\textbf{Email:} \href{mailto:carlamm@ksu.edu}{\tt carlamm@ksu.edu}. \textbf{Contact:} Department of Political Science, 101D Calvin Hall, Kansas State University, Manhattan, KS 66506.} \\
Department of Political Science \\
Kansas State University \\
\and Andrew Stravers\thanks{\textbf{Email:} \href{mailto:stravers@utexas.edu}{\tt stravers@utexas.edu}. \textbf{Contact:} The University of Texas at Austin, 158 W 21st ST STOP A1800, Batts Hall 2.116, Austin, TX 78712-1704}\\
Department of Government\\
University of Texas--Austin \\
\and
Michael A. Allen\thanks{\textbf{Email:} \href{mailto:michaelaallen@boisestate.edu }{\tt michaelaallen@boisestate.edu }. \textbf{Contact:} Department of Political Science, Boise State University, 1910 University Drive, Boise, ID 83725.}\\
Department of Political Science\\
Boise State University \\
\and
Michael E. Flynn\thanks{\textbf{Email:} \href{mailto:meflynn@ksu.edu}{\tt meflynn@ksu.edu}. \textbf{Contact:} Department of Political Science, 019C Calvin Hall, Kansas State University, Manhattan, KS 66506.}\\
Department of Political Science\\
Kansas State University
}

\maketitle
\thispagestyle{empty}

%\begin{center}
% \textcolor{red}{WORKING PAPER. PLEASE DO NOT CITE}
%\end{center}

\clearpage

\begin{abstract}
What are the determinants of anti-military base protests abroad?  Are they different from anti-American protests in general?  How does the context of the deployment influence the level of protest against it in the host country?  Using newly-collected events data for the years 1990 to 2018 on protest events around the world we explain the circumstance that make anti-basing protests, as well as anti-U.S. protests, more likely to occur. We argue that anti-U.S. protests are more likely to occur when they are seen as more permanent installations that are independent of domestic military forces.  In addition, previous work finds that direct contact with military personnel leads to more positive perceptions of the U.S. military in host states. Thus, we expect to see more anti-base protests in locations that are more easily accessible (close to urban centers) to transnational activists, rather than only to locals. We thus expect to observe more protests against bases that are close to urban centers.  
\end{abstract}



\vfill

\titlespacing{\section}{0pt}{*2}{*0}
\titlespacing{\subsection}{0pt}{*2}{*0}
\titlespacing{\subsubsection}{0pt}{1cm}{*0}

\thispagestyle{empty}


\newpage
\setcounter{page}{1}
\doublespacing
\input{introProtest}
\input{theoryProtest}
\input{rdProtest}
\input{resultsProtest}
\input{conclusionProtest}


\newpage

%\bibliographystyle{apsr01}
\bibliography{one}

%\newpage
%\input{appendixProtest}

\end{document}