---
title: "chapter-protest-assembly"
author: "Michael Flynn"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

# Front Matter

This section loads the data files and libraries. Assembles the main data.

## Notes:

1. I parsed out the imports and exports initial lines because the subsequent code chunks act super weird. 

2. I rewrote almost all of this on May 8, 2020 after similarly reworking the code from the Republican foreign policy book project. The main changes were:
    - Replacing the GDP data with Gleditsch's expanded trade and GDP data up through 2011.
    - Using Penn World Tables data from 2012-2018
    - Replacing trade data with COW trade data up through 2012
    - Using IMF trade data for 2013-2018
    - I also updated the troops data to include troops located in the continental United States. This affects Russia and Canada's spatial measures of troops.
    
    
# Code frontmatter

```{r setup , include = FALSE, ecno = FALSE}
library(tidyverse)
library(here)
library(cshapes)
library(countrycode)
library(arm)
library(tidyquant)
library(readxl)
library(psych)



```



# Read and clean data

```{r data assembly, echo = FALSE, warning=FALSE}

# Read and clean data

#### Base dyads ####



#Please note that the PRIO armed conflict data is available from this website: https://ucdp.uu.se/downloads/
  
# Read and clean data
# US protest events only
event.list <- c("Protest altruism", "Protest defacement", "Protest demonstrations", "Protest obstruction", "Protest procession", "Strikes and boycotts", "Threaten to boycott or embargo")

protest.us <- readxl::read_xlsx(here::here("Raw Data", "_Revised Extractions and Events.xlsx"), sheet = 2) %>%  
  filter(`Protest Event` %in% event.list) %>% 
  mutate(miltarget = if_else(TgtSector == "<MILI>", 1, 0),
         ustarget = if_else(TgtCountry == "USA", 1, 0),
         antiusmil = if_else(miltarget == 1 & ustarget == 1, 1, 0),
         year = format(as.Date(EventDate, format = "%Y-%m-%d"), "%Y"),
         month = format(as.Date(EventDate, format = "%Y-%m-%d"), "%b")) %>% 
  mutate(ccode = countrycode(Location, "country.name", "cown")) %>% 
  group_by(ccode, year, month, ID) %>% 
  mutate(duplicates = seq()) %>% 
  group_by(ccode, year) %>% 
  summarise(anti_us_protest = sum(ustarget, na.rm = TRUE),
            anti_us_mil = sum(antiusmil, na.rm = TRUE)) %>% 
  mutate(year = as.numeric(year))


# All protest events (denominator)
protest.base <- readxl::read_xlsx(here("Raw Data", "Foreign Protest Monthly Counts.xlsx")) %>% 
  filter(Event %in% event.list) %>% 
  mutate(ccode = countrycode(Country, "country.name", "cown")) %>%
  group_by(ccode, Year) %>% 
  summarise(protest_count = sum(Count, na.rm = TRUE)) %>%
  rename("year" = "Year") %>% 
  filter(!is.na(ccode))


# Country-year list
cyear.base <- read_csv(here("Raw Data", "system2016 (2).csv")) %>%
  filter(year >= 1988) %>% 
  dplyr::select(ccode, year)


# Protest combined 
protest.combined <- cyear.base %>% 
  left_join(protest.base, by = c("ccode", "year")) %>% 
  left_join(protest.us, by = c("ccode", "year")) %>% 
  mutate(protest_count = if_else(is.na(protest_count), 0, protest_count),
         anti_us_protest = if_else(is.na(anti_us_protest), 0, anti_us_protest),
         anti_us_mil = if_else(is.na(anti_us_mil), 0, anti_us_mil),
         protest_other = (protest_count - anti_us_protest - anti_us_mil),
         protest_other = ifelse(protest_other < 0, 0, protest_other),
         country = countrycode(ccode, "cown", "country.name"))


# Protest data frame for spatial var
protest.sp <- protest.combined %>% 
  rename("ccode2" = "ccode")


# Use the countrycode base dataframe. Reconciled so each unit appears once per country year.
panelcodes <- countrycode::codelist_panel


# Gleditsch Expanded Trade and GDP v6.0
# Real GDP in 2005 Dollars
# First reading in CPI data for all urban consumers and converting 2011 to base year to match PWT data.
cpi <- tq_get("CPIAUCSL", 
              get = "economic.data",
              from = "1950-01-01",
              to = "2019-01-01") %>% 
  mutate(year = format(date, "%Y")) %>% 
  group_by(year) %>% 
  summarise(cpi = mean(price)) %>% 
  mutate(basevalue = cpi[year==2011], # Set new base year value of 2011 to put GDP values on same scale
         cpi = cpi/basevalue,
         year = as.numeric(year))


gled.data <- read_delim(here("Raw Data/expgdpv6.0", "gdpv6.txt"), delim = "\t") %>% 
  rename("ccode" = "statenum") %>% 
  left_join(cpi, by = "year") %>% 
  mutate(realgdp_merge = ((pop*1000)*cgdppc)/cpi,
         pop = pop/1000)


# Final data frame containing merge PWT and Gleditsch data
gdp.data <- peacesciencer::create_stateyears(system = "gw") %>% 
  add_sdp_gdp() %>% 
  dplyr::rename("ccode" = "gwcode") %>% 
  filter(year >= 1990) %>% 
  mutate(ccode = ifelse(ccode == 260, 255, ccode))


gdp.data.wdi <- wbstats::wb_data(country = "countries_only",
                     indicator = c("pop" = "SP.POP.TOTL", "gdp" = "NY.GDP.MKTP.KD"),
                     start_date = 1989,
                     end_date = 2018,
                     return_wide = TRUE)  %>% 
  mutate(ccode = countrycode(country, "country.name", "cown")) %>%
  dplyr::rename("year" = "date") %>% 
  mutate(gdp.wb = log(gdp),
         pop.wb = log(pop))


gdp.com <- gdp.data %>% 
  full_join(gdp.data.wdi) 


gdpcheck <- ggplot(gdp.com %>% filter(ccode %in% c(2, 40, 70, 200, 210, 255, 645, 700, 710, 740, 732, 365)), aes(x = year)) +
  geom_line(aes(y = wbpop2011est, color = "SDPGDP")) +
  geom_line(aes(y = gdp.wb, color = "Update")) +
  facet_wrap(~ statename)

gdpcheck

# Spatial GDP Data Frame 
gdp.sp <- gdp.com %>% 
  dplyr::rename("ccode2" = "ccode")


# V-Dem Data
vdem.data <- read_csv(here::here("Raw Data", "V-Dem-CY-Core-v11.1.csv")) %>% 
  dplyr::select("country_name", "year", "v2x_polyarchy", "v2x_libdem", "COWcode") %>% 
  filter(year >= 1950) %>% 
  rename("ccode" = "COWcode") %>% 
  mutate(ccode = ifelse(ccode == 260, 255, ccode))



#### Gleditsch Trade Data ####
trade.gled <- read_delim(here::here("Raw Data/trade_dd.asc"), delim = " ") %>% 
  filter(numa %in% c(2)) %>% 
  filter(year >= 1950) %>% 
  dplyr::rename("ccode1" = "numa", "ccode2" = "numb", "imports_to_ccode1_g" = "impab",  "exports_from_ccode1_g" = "expab") %>% 
  mutate(ccode2 = ifelse(ccode2 == 260, 255, ccode2)) 
  

#### COW Trade Data ####

trade.cow.data <- read_csv(here::here("Raw Data/Dyadic_COW_4.0.csv")) %>%
  filter(year >= 1950 & ccode1 %in% c(2)) %>%
  dplyr::mutate(flow1 = ifelse(flow1 == -9, NA, flow1),
                flow2 = ifelse(flow2 == -9, NA, flow2)) %>% 
  dplyr::rename("imports_to_ccode1_cow" = "flow1",
                "exports_from_ccode1_cow" = "flow2") %>%
  dplyr::select("ccode1", "ccode2","year", "imports_to_ccode1_cow", "exports_from_ccode1_cow") %>% 
  mutate(ccode2 = case_when(
    ccode2 == 260 ~ 255,
    TRUE ~ ccode2
  )) 


# Combine trade data for COW and Gleditsch
trade.com <- trade.cow.data %>% 
  full_join(trade.gled) %>% 
  mutate(across(starts_with("imports|exports"), ~round(.x, digits = 4))) %>% 
  dplyr::rename("ccode" = "ccode2") %>% 
  dplyr::select(-c("ccode1"))



# WARNING!!! for whatever reason the pivot function sometimes doesn't work on every other pass. 
# Make sure this is in long form

# Also, LOTS of stupid names match the Netherlands country codes. Filter those out.
netherlandsfilter <- c("Curaçao, Kingdom of the Netherlands", "Sint Maarten, Kingdom of the Netherlands", "Aruba, Kingdom of the Netherlands")

`%notin%` <- Negate(`%in%`) # create this to get rid of lots of duplicate Netherlands values. Appear as a result of protectorates or territories. 

# IMF DOTS Exports to counterpart countries from US
# Note that file (5) contains only more recent IMF data for 2014 - 2018.
# File (6) contains info from 1950 forward.
exports.data <- read_xlsx(here::here("Raw Data", "Exports_and_Imports_by_areas_and_Co (6).xlsx"), sheet = 1, skip = 5)

exports.data <- exports.data %>% 
  rename("country" = 1) %>% 
  pivot_longer(cols = 2:ncol(exports.data),
               values_to = "exports",
               names_to = "year") %>% 
  filter(country %notin% netherlandsfilter) %>% 
  mutate(ccode = countrycode(country, "country.name", "cown"),
         ccode = ifelse(country == "Eastern Germany", 265, ccode),
         ccode = ifelse(country == "China, P.R.", 710, ccode),
         ccode = ifelse(country == "Central African Rep.", 482, ccode),
         year = as.numeric(year)) %>% 
#  filter(year > 2014) %>% 
  rename("exports_from_ccode1_imf" = "exports") %>% 
  dplyr::select("ccode", "year", "exports_from_ccode1_imf")


# IMF DOTS Imports from counterpart countries into US
imports.data <-read_xlsx(here::here("Raw Data", "Exports_and_Imports_by_areas_and_Co (6).xlsx"), sheet = 2, skip = 5)

imports.data <- imports.data %>% 
  rename("country" = 1) %>% 
  pivot_longer(cols = 2:ncol(imports.data),
               values_to = "imports",
               names_to = "year") %>% 
  filter(!(country %in% netherlandsfilter)) %>% 
  mutate(ccode = countrycode(country, "country.name", "cown"),
         ccode = ifelse(country == "Eastern Germany", 265, ccode),
         ccode = ifelse(country == "China, P.R.", 710, ccode),
         ccode = ifelse(country == "Central African Rep.", 482, ccode),
         year = as.numeric(year)) %>% 
#  filter(year > 2014) %>% 
  rename("imports_to_ccode1_imf" = "imports") %>% 
  dplyr::select("ccode", "year", "imports_to_ccode1_imf")

imf.combined <- exports.data %>% 
  full_join(imports.data, by = c("ccode", "year")) %>% 
  filter(!is.na(ccode))

# Combine COW and IMF trade data
# Combine COW and IMF trade data for US and Russia ####
trade.data.final <- trade.com %>%
  full_join(imf.combined) %>%
  filter(!is.na(ccode)) %>%
  arrange(ccode, year) %>% 
  mutate(tick = 1) %>% 
  group_by(ccode, year) %>% 
  dplyr::mutate(dups = cumsum(tick)) %>% 
  dplyr::arrange(-dups) %>% 
  filter(dups == 1) %>% 
  left_join(cpi, by = "year") %>%
  mutate(exports_from_us = case_when(
           !is.na(exports_from_ccode1_imf) ~ exports_from_ccode1_imf,
           is.na(exports_from_ccode1_imf) ~ exports_from_ccode1_cow,
           is.na(exports_from_ccode1_cow) ~ exports_from_ccode1_g
         ),
         imports_to_us = case_when(
           !is.na(imports_to_ccode1_imf) ~ imports_to_ccode1_imf,
           is.na(imports_to_ccode1_imf) ~ imports_to_ccode1_cow,
           is.na(imports_to_ccode1_cow) ~ imports_to_ccode1_g),
         across(contains("_us"),  ~.x/cpi))

# Check trade data comparison
tradecheck <- ggplot(data = trade.data.final %>% filter(ccode %in% c(20, 200, 210, 211, 212, 325, 390, 220, 255, 356, 640, 645, 710, 732, 740, 900)), aes(x = year)) +
  geom_line(aes(y = exports_from_ccode1_cow, color = "COW"), size = 2) +
  geom_line(aes(y = exports_from_ccode1_g, color = "Gleditsch"), size = 1.2) +
  geom_line(aes(y = exports_from_ccode1_imf, color = "IMF"), size = 1.2) +
  geom_line(aes(y = exports_from_us, color = "Selected"), size = 4, alpha = 0.7) +
  facet_wrap(. ~ ccode) +
  scale_x_continuous(breaks = seq(1950, 2020, 10))

tradecheck

# Create second data frame for spatial analysis
trade.data.sp <- trade.data.final %>% 
  rename("ccode2" = "ccode")


# Load foreign aid data from US AID Green book
aid.base <- readxl::read_xlsx(here("Raw Data", "us_foreignaid_greenbook.xlsx"), skip = 6)

# Rename the columns
names(aid.base) <- c("year", "region", "country", "category", "pubrow", "agency", "account", "aid.current", "aid.constant")


# Create county-year tibble
time <- tibble(ccode2 = 2:999) %>% 
  mutate(ccode = countrycode(ccode2, "cown", "cown"),
         year = list(seq(from = 1949, to = 2018))) %>% 
  filter(!is.na(ccode) & ccode != 2) %>% 
  select("ccode", "year") %>% 
  unnest(cols = c(year))


# Read in and edit aid data
aid.data <- aid.base %>% 
  mutate(year = ifelse(year == 1976.9, year == 1976, year)) %>% 
  group_by(country, year, category) %>% 
  summarise(aid.constant = sum(aid.constant, na.rm = TRUE),
            aid.current = sum(aid.current, na.rm = TRUE)) %>% 
  dplyr::select(-c(5)) %>% 
  pivot_wider(names_from = category,
              values_from = aid.constant) %>% 
  ungroup() %>% 
  mutate(ccode = countrycode(country, "country.name", "cown")) %>% 
  filter(!is.na(ccode)) %>% 
  full_join(time) %>% 
  mutate(Economic = ifelse(is.na(Economic), 0, Economic),
         Military = ifelse(is.na(Military), 0, Military),
         log_econ = log(Economic + 1),
         log_mil = log(Military + 1)) %>% 
  rename("econaid" = "Economic", "milaid" = "Military") %>% 
  arrange(ccode, year) %>% 
  mutate(country = countrycode(ccode, "cown", "country.name"))


# SIPRI Data
sipri.data <- read_xlsx(here::here("Raw Data/SIPRI-Milex-data-1949-2019.xlsx"), sheet = 7, skip = 4)

sipri.data <- sipri.data %>% 
  pivot_longer(cols = c(3:73),
               names_to = "year",
               values_to = "defburden") %>%
  filter(year >= 1988) %>% 
  mutate(ccode = countrycode(Country, "country.name", "cown")) %>% 
  mutate(ccode = ifelse(Country == "German DR", 265,
                        ifelse(Country == "Serbia", 345,
                               ifelse(Country == "Central African Rep.", 482, ccode)))) %>% 
  filter(defburden != "xxx" & defburden != ". .") %>% 
  mutate(defburden = round(as.numeric(defburden), digits = 4)) %>% 
  select(ccode, year, defburden) %>% 
  mutate(year = as.numeric(year))

sipri.sp <- sipri.data %>% 
  rename("ccode2" = "ccode")
  
  
  


# PRIO Data
# https://ucdp.uu.se/downloads/
prio.data <- read_csv(here("Raw Data/ucdp-prio-acd-191.csv")) %>% 
  rowwise() %>% 
  dplyr::select("conflict_id", "year", "intensity_level", "gwno_loc") %>% 
  separate(gwno_loc, sep = ",", into = c("ccode1", "ccode2", "ccode3", "ccode4" ,"ccode5", "ccode6")) %>% 
  pivot_longer(cols = c("ccode1", "ccode2", "ccode3", "ccode4", "ccode5", "ccode6"), 
               names_to = "countrynum", 
               values_to = "ccode", 
               values_drop_na = TRUE,
               names_repair = "minimal") %>% 
  mutate(ccode = as.numeric(trimws(ccode, which = "both")),
         intensity.low = if_else(intensity_level == 1, 1, 0),
         intensity.high = if_else(intensity_level == 2, 1, 0)) %>% 
  group_by(ccode, year) %>% # Gleditsch and Ward location country code and year
  dplyr::summarise(conflictcount = n_distinct(conflict_id),
            conflictcount_high = sum(intensity.high, na.rm = TRUE),
            conflictcount_low = sum(intensity.low, na.rm = TRUE),
            conflict_dummy = if_else(conflictcount > 0, 1, 0)) %>% 
  filter(year >= 1950) %>% 
  dplyr::rename("ccode2" = "ccode")


# PRIO data for spatial analysis
prio.sp <- prio.data 
  

# US War data using PRIO data
prio.us <- read_csv(here("Raw Data/ucdp-prio-acd-191.csv")) %>% 
  rowwise() %>% 
  mutate(us_war = ifelse(grepl(".*United States.*", side_a), 1, 
                             ifelse(grepl(".*United States.*", side_a_2nd), 1,
                                    ifelse(grepl(".*United States", side_b), 1,
                                           ifelse(grepl(".*United States.*", side_b_2nd), 1, 0))))) %>% 
  filter(us_war == 1) %>% 
  select("location", "conflict_id", "year", "intensity_level", "gwno_loc", "us_war") %>% 
  separate(gwno_loc, sep = ",", into = c("ccode1", "ccode2", "ccode3", "ccode4" ,"ccode5", "ccode6")) %>% 
  pivot_longer(cols = c("ccode1", "ccode2", "ccode3", "ccode4", "ccode5", "ccode6"), 
               names_to = "countrynum", 
               values_to = "ccode", 
               values_drop_na = FALSE,
               names_repair = "minimal") %>% 
  mutate(ccode = as.numeric(trimws(ccode, which = "both"))) %>% 
  filter(!is.na(ccode) & ccode != 2) %>% 
  select(year, ccode, us_war) %>% 
  group_by(ccode, year) %>% 
  summarise(us_war = max(us_war, na.rm = TRUE)) %>% 
  filter(year >= 1950)

# Spatial data sets
prio.us.sp <- prio.us %>% 
  rename("ccode2" = "ccode")



# Troop deployment data
troops.data.combined <- troopdata::troopdata %>% 
  group_by(ccode) %>% 
  mutate(log_troops = log1p(troops),
         log_troops = ifelse(is.finite(log_troops), log_troops, NA), # remove NaN and Inf values
         troops_change = ifelse(!is.na(troops) & !is.na(dplyr::lag(troops)), as.numeric(troops - dplyr::lag(troops)), NA),
         troops_change = ifelse(is.finite(troops_change), troops_change, NA)) # remove NaN and Inf values


# Create second data frame for troops data for spatial weighting
troops.sp <- troops.data.combined %>% 
  filter(year >= 1950) %>% 
  dplyr::select("ccode", "year", "troops") %>% 
  dplyr::rename("ccode2" = "ccode")


# UN Ideal Point Data
undata <- read_delim(here("Raw Data", "Idealpoints.tab"), delim = "\t") %>% # Tab delimited
  dplyr::select(ccode, idealpoint, year) %>% 
  dplyr::filter(year >= 1950) %>% 
  mutate(ccode2 = list(seq(2:999))) %>% 
  unnest(ccode2)


undata.2 <- read_delim(here("Raw Data", "Idealpoints.tab"), delim = "\t") %>% # Tab delimited
  dplyr::select(ccode, idealpoint, year) %>% 
  dplyr::filter(year >= 1950) %>% 
  rename("ccode2" = "ccode")


undata.com <- undata %>% 
  full_join(undata.2, by = c("ccode2", "year")) %>% 
  dplyr::arrange(ccode, ccode2, year) %>% 
  dplyr::filter(!is.na(idealpoint.y)) %>% 
  dplyr::filter(ccode2 == 2 | ccode2 == 365) %>% 
  mutate(idealdistance = abs(idealpoint.x - idealpoint.y)) %>% 
  dplyr::select(ccode, ccode2, year, idealdistance) %>% 
  pivot_wider(id_cols = c(ccode, year),
              values_from = "idealdistance",
              names_from = "ccode2",
              names_prefix = "idealdistance_") %>% 
  dplyr::filter(ccode != 2) %>% 
  mutate(ccode = ifelse(ccode == 260, 255, ccode)) %>% 
  group_by(ccode, year) %>% 
  arrange(ccode, year) 


# ATOP alliance data
ally.data <- read_csv(here("Raw Data/ATOP V4.01 Data (csv)", "atop4_01ddyr.csv")) %>% 
  dplyr::select(stateA, stateB, year, defense, offense) %>% 
  dplyr::filter(stateA == 2,
         year >= 1950) %>% 
  mutate(us_ally = ifelse(defense == 1 | offense == 1, 1, 0),
         stateB = ifelse(stateB == 260, 255, stateB)) %>% 
  dplyr::select(stateB, year, us_ally) %>% 
  dplyr::rename("ccode" = "stateB") %>% 
  group_by(ccode,  year) %>% 
  dplyr::summarise(us_ally = max(us_ally, na.rm = TRUE)) # Get rid of Germany duplicate

ally.sp <- ally.data %>% 
  dplyr::rename(ccode2 = ccode)

# Create spatial weighting framework for troops variable
# This only goes up to 2016 so we have to hack the last two years and assume everything is the same re distance
# Create mindist data ####

if (file.exists(here::here("Raw Data/mindist-dataframe.csv"))) {
  
  mindist.df <- read_csv(here::here("Raw Data/mindist-dataframe.csv"))
  
} else {

  startdate = as.Date("1988-01-01", format = "%Y-%m-%d")
  enddate = as.Date("2018-01-01", format = "%Y-%m-%d")
  datelist <- data.frame(date = as.Date(seq(startdate, enddate, by = "1 year"), format = "%y-%m-%d"))

  thedate <- startdate

  mindist <- as.list(datelist$date) # Create empty list 

  mindist <- lapply(mindist, function(x) 
    df <- cshapes::distlist(date = x, type = "mindist", keep = 0.1, useGW = FALSE) %>% 
      mutate(year = x)
  )

  mindist.df <- bind_rows(mindist) %>% 
    mutate(year = format(year, "%Y"))

  write.csv(mindist.df, here::here("Raw Data/mindist-dataframe.csv"))

}



# Create minimum distance dataframe to merge troops data
# Note that the data only go through 2016. Must replicate 2017 and 2018.
mindist.df <- bind_rows(mindist) %>% 
  mutate(year = as.numeric(format(year, "%Y"))) %>% 
  filter(ccode1 != ccode2) %>% 
  mutate(ccode1 = ifelse(ccode1 == 260, 255, ccode1),
         ccode2 = ifelse(ccode2 == 260, 255, ccode2),
         mindist = ifelse(mindist < 1, 0, mindist), # Note: distlist is returning weird values < 1 & > 0. These all appear to be contiguous.
         mindist450k = ifelse(mindist == 0, 1, 
                              ifelse(mindist > 450, NA, mindist))) %>% 
  left_join(troops.sp, by = c("ccode2", "year")) %>%
  left_join(prio.sp, by = c("ccode2", "year")) %>% 
  left_join(prio.us.sp, by = c("ccode2", "year")) %>% 
  left_join(trade.data.sp, by = c("ccode2", "year")) %>% 
  left_join(protest.sp, by = c("ccode2", "year")) %>% 
  left_join(sipri.sp, by = c("ccode2", "year")) %>% 
  left_join(ally.sp, by = c("ccode2", "year")) %>% 
  arrange(ccode1, ccode2, year) %>% 
  mutate(us_war = ifelse(is.na(us_war), 0, us_war),
         us_ally = ifelse(is.na(us_ally), 0, us_ally),
         conflictcount = ifelse(is.na(conflictcount), 0, conflictcount),
         conflictcount_high = ifelse(is.na(conflictcount_high), 0, conflictcount_high),
         conflictcount_low = ifelse(is.na(conflictcount_low), 0, conflictcount_low),
         conflict_dummy = ifelse(is.na(conflict_dummy), 0, conflict_dummy),
         inversedistance = if_else(mindist450k > 0, (1 / mindist450k), 0),
         troops_w = inversedistance * troops,
         us_ally_w = inversedistance * us_ally,
         us_war_w = inversedistance * us_war,
         conflictcount_w = inversedistance * conflictcount,
         conflictcount_high_w = inversedistance * conflictcount_high,
         conflictcount_low_w = inversedistance * conflictcount_low,
         conflict_dummy_w = inversedistance * conflict_dummy,
         imports_to_us_w = inversedistance * imports_to_us,
         exports_from_us_w = inversedistance * exports_from_us,
         protest_count_w = inversedistance * protest_count,
         protest_other_w = inversedistance * protest_other,
         anti_us_protest_w = inversedistance * anti_us_protest,
         anti_us_mil_w = inversedistance * anti_us_mil,
         defburden_w = inversedistance * defburden) %>% # Look only at variables within 450k of the referent state
  arrange(ccode1, ccode2, year) %>% 
  group_by(ccode1, year) %>% 
  dplyr::summarise(troops_w_sum = sum(troops_w, na.rm = TRUE),
                   troops_w_mean = mean(troops_w, na.rm = TRUE),
                   us_war_w_mean = mean(us_war_w, na.rm = TRUE),
                   us_ally_w_mean = mean(us_ally_w, na.rm = TRUE),
                   conflictcount_w_mean = mean(conflictcount_w, na.rm = TRUE),
                   conflictcount_high_w_mean = mean(conflictcount_high_w, na.rm = TRUE),
                   conflictcount_low_w_mean = mean(conflictcount_low_w, na.rm = TRUE),
                   conflict_dummy_w_mean = mean(conflict_dummy_w, na.rm = TRUE),
                   imports_to_us_w_mean = mean(imports_to_us_w, na.rm = TRUE),
                   exports_from_us_w_mean = mean(exports_from_us_w, na.rm = TRUE),
                   protest_count_w_mean = mean(protest_count_w, na.rm = TRUE),
                   protest_other_w_mean = mean(protest_other_w, na.rm = TRUE),
                   anti_us_protest_w_mean = mean(anti_us_protest_w, na.rm = TRUE),
                   anti_us_mil_w_mean = mean(anti_us_mil_w, na.rm = TRUE),
                   defburden_w_mean = mean(defburden_w, na.rm = TRUE)) %>% 
  mutate(troops_w_sum = ifelse(is.finite(troops_w_sum), troops_w_sum, NA),
         troops_w_mean = ifelse(is.finite(troops_w_mean), troops_w_mean, NA),
         us_war_w_mean = ifelse(is.finite(us_war_w_mean), us_war_w_mean, NA),
         us_ally_w_mean = ifelse(is.finite(us_ally_w_mean), us_ally_w_mean, NA),
         conflictcount_w_mean = ifelse(is.finite(conflictcount_w_mean), conflictcount_w_mean, NA),
         conflictcount_high_w_mean = ifelse(is.finite(conflictcount_high_w_mean), conflictcount_high_w_mean, NA),
         conflictcount_low_w_mean = ifelse(is.finite(conflictcount_low_w_mean), conflictcount_low_w_mean, NA),
         conflict_dummy_w_mean = ifelse(is.finite(conflict_dummy_w_mean), conflict_dummy_w_mean, NA),
         imports_to_us_w_mean = ifelse(is.finite(imports_to_us_w_mean), imports_to_us_w_mean, NA),
         exports_from_us_w_mean = ifelse(is.finite(exports_from_us_w_mean), exports_from_us_w_mean, NA),
         protest_count_w_mean = ifelse(is.finite(protest_count_w_mean), protest_count_w_mean, NA),
         protest_other_w_mean = ifelse(is.finite(protest_other_w_mean), protest_other_w_mean, NA),
         anti_us_protest_w_mean = ifelse(is.finite(anti_us_protest_w_mean), anti_us_protest_w_mean, NA),
         anti_us_mil_w_mean = ifelse(is.finite(anti_us_mil_w_mean), anti_us_mil_w_mean, NA),
         defburden_w_mean = ifelse(is.finite(defburden_w_mean), defburden_w_mean, NA)) %>% 
  filter(ccode1 != 2) %>% 
  dplyr::rename("ccode" = "ccode1")



# Create a time series frame with the total size of the US military by year
# Military size 1954-1993

milsize.1950.2005 <- readxl::read_xls(here::here("Raw Data", "troopMarch2005.xls"), sheet = 2) %>% # Kane's Heritage data.
  slice(6) %>% 
  dplyr::select(-1) %>% 
  mutate_if(is.numeric, as.character) %>% # Some conflicting types after reading data in
  group_by(Country) %>% 
  pivot_longer(cols = 2:57,
               values_to = "troops",
               names_to = "year") %>% 
  dplyr::select(Country, year, troops) %>% 
  mutate_each(funs = as.numeric) %>% # Convert all to numeric for append 
  filter(year <= 1993) 


# Military size 1994-2012

milsize <- readxl::excel_sheets(here::here("Raw Data", "AD_Strengths_FY1994-FY2012.xlsx"))

milsize.list <- lapply(milsize, function(x) readxl::read_excel(here::here("Raw Data", "AD_Strengths_FY1994-FY2012.xlsx"), sheet = x))

milsize.1.df <- bind_rows(milsize.list) %>% 
  filter(grepl(".*GRAND TOTAL.*", Rank)) %>% 
  dplyr::select("DoD Total") %>% 
  mutate(year = seq(1994, 2012)) %>% 
  dplyr::rename("Total" = "DoD Total") %>% 
  mutate(troops = as.numeric(Total),
         year = as.numeric(year)) %>% 
  dplyr::select(troops, year)

# Military size 2013-2016
milsize <- readxl::excel_sheets(here::here("Raw Data", "AD_Strengths_FY2013-FY2016.xlsx"))

milsize.list <- lapply(milsize, function(x) readxl::read_excel(here::here("Raw Data", "AD_Strengths_FY2013-FY2016.xlsx"), sheet = x))

milsize.2.df <- bind_rows(milsize.list) %>% 
  filter(grepl(".*GRAND TOTAL.*", `Department of Defense`)) %>% 
  dplyr::rename("Total" = 6) %>% 
  dplyr::select("Total") %>% 
  mutate(year = seq(2013, 2016)) %>% 
  mutate(troops = as.numeric(Total),
         year = as.numeric(year)) %>% 
  dplyr::select(troops, year)



# 2017 and 2018 data

# Troops 2017 (includes active duty only)
milsize.2017 <- readxl::read_xlsx(here::here("Raw Data", "DMDC_Website_Location_Report_1712.xlsx"), skip = 5) %>% 
  filter(grepl(".*GRAND.*", LOCATION)) %>% 
  dplyr::select(8) %>% 
  dplyr::rename("troops" = 1) %>% 
  mutate(year = 2017) %>% 
  mutate_each(as.numeric)


# Troops 2018 (includes active duty only)
milsize.2018 <- readxl::read_xlsx(here::here("Raw Data", "DMDC_Website_Location_Report_1812.xlsx"), skip = 5) %>% 
  filter(grepl(".*GRAND.*", LOCATION)) %>% 
  dplyr::select(8) %>% 
  dplyr::rename("troops" = 1) %>% 
  mutate(year = 2018) %>% 
  mutate_each(as.numeric)


milsize.1950.2018 <- bind_rows(milsize.1950.2005, milsize.1.df, milsize.2.df, milsize.2017, milsize.2018) %>% 
  rename("usmilsize" = "troops")





# US Government Composition Data
# The President chamber is missing from the 115th and 116th congresses. Code looks a little wild partly due to this. Also having to generate years.
nom.data <- read_csv(here("Raw Data", "HSall_members.csv")) %>% 
  filter(congress >= 81) %>% 
  group_by(congress, chamber) %>% 
  mutate(seats = n_distinct(paste(state_icpsr, district_code)),
         reppres = ifelse(party_code == 200 & chamber == "President", 1, 0),
         repmem = ifelse(party_code == 200, 1, 0)) %>% 
  summarise(seats = max(seats, na.rm = TRUE),
            repseats = sum(repmem),
            reppres = max(reppres, na.rm = TRUE)) %>% 
  group_by(chamber) %>% 
  mutate(seats = ifelse(chamber == "Senate", seats * 2, seats),
         seats = ifelse(chamber == "House", 435, seats),
         repseatshare = repseats/seats) %>% 
  pivot_wider(values_from = c("seats", "repseats", "repseatshare", "reppres"),
              names_from = "chamber") %>% 
  mutate(session = list(seq(1:2))) %>% 
  unnest(session) %>% 
  mutate(year = seq(1949, 2020, by = 1),
         reppres = reppres_President,
         reppres = ifelse(congress == 114, 0, reppres),
         reppres = ifelse(congress == 116, 1, reppres),
         repseatshare_change_house = repseatshare_House - dplyr::lag(repseatshare_House, order_by = congress),
         repseatshare_change_house = ifelse(repseatshare_change_house == 0, dplyr::lag(repseatshare_change_house), repseatshare_change_house),
         repseatshare_change_senate = repseatshare_Senate - dplyr::lag(repseatshare_Senate, order_by = congress),
         repseatshare_change_senate = ifelse(repseatshare_change_senate == 0, dplyr::lag(repseatshare_change_senate), repseatshare_change_senate)) %>% 
  dplyr::select("congress", "year", "seats_House", "seats_Senate", "repseats_House", "repseats_Senate", "repseatshare_House", "repseatshare_change_house", "repseatshare_change_senate", "repseatshare_Senate", "reppres") %>% 
  rename("seats_house" = "seats_House", "seats_senate" = "seats_Senate", "repseats_house" = "repseats_House", "repseats_senate" = "repseats_Senate", "repseatshare_house" = "repseatshare_House", "repseatshare_senate" = "repseatshare_Senate")
  

# Create function to rescale variables by dividing by 1 million
scale1k <- function(x, na.rm = FALSE) (x/1000)
scale1m <- function(x, na.rm = FALSE) (x/1000000)

# Combine data into single data frame
protest.data.final <- vdem.data %>% 
  left_join(aid.data, by = c("ccode", "year")) %>% 
  left_join(gdp.data, by = c("ccode", "year")) %>% 
  left_join(trade.data.final, by = c("ccode", "year")) %>% 
  left_join(protest.combined, by = c("ccode", "year")) %>% 
  left_join(mindist.df, by = c("ccode", "year")) %>%
  left_join(troops.data.combined, by = c("ccode", "year")) %>% 
  left_join(undata.com, by = c("ccode", "year")) %>% 
  left_join(ally.data, by = c("ccode", "year")) %>% 
  left_join(prio.data, by = c("ccode", "year")) %>% 
  left_join(prio.us, by = c("ccode", "year")) %>% 
  left_join(sipri.data, by = c("ccode", "year")) %>% 
  left_join(milsize.1950.2018) %>% 
  left_join(nom.data, by = c("year")) %>% 
  dplyr::select(-c("country.y", "country_name")) %>% 
  dplyr::rename("country" = "country.x") %>% 
  mutate(us_ally = ifelse(is.na(us_ally), 0, us_ally),
         us_war = ifelse(is.na(us_war), 0, us_war),
         conflict_dummy = ifelse(is.na(conflict_dummy), 0, conflict_dummy)) %>% 
  group_by(ccode) %>% 
  mutate(exposure = n()) %>% # Generate exposure variable for models. Number of observatiosn for each country.
  mutate_at(vars("gdp", "pop","exports_from_us", "imports_to_us"),
            list(growth = ~((((.) - dplyr::lag(., order_by = year)) / dplyr::lag(., order_by = year))))) %>% 
  mutate_at(vars("pop","gdp", "v2x_polyarchy", "econaid", "milaid", "v2x_libdem", "imports_to_us", "exports_from_us", "pop_rescaled", "gdp_rescaled", "milaid_rescaled", "econaid_rescaled", "exports_from_us_rescaled", "imports_to_us_rescaled", "idealdistance_2", "idealdistance_365", "troops_w_sum", "troops_w_mean", "troops_w_mean_rescaled", "troops_w_sum_rescaled", "us_war_w_mean", "protest_count_w_mean", "anti_us_protest_w_mean", "anti_us_mil_w_mean"),
            list(change = ~ ifelse(is.finite(.), (.) - dplyr::lag(., order_by = year), NA))) %>% # weed out Inf and NaN values.
  mutate_at(vars("pop", "gdp", "v2x_polyarchy", "econaid", "milaid", "milaid_change", "troops_rescaled", "v2x_libdem", "imports_to_us", "exports_from_us", "idealdistance_2", "idealdistance_365", "troops", "troops_w_sum", "troops_w_mean", "troops_w_mean_change", "conflict_dummy", "us_war", "us_ally", "us_war_w_mean", "protest_count_w_mean", "anti_us_protest_w_mean", "anti_us_mil_w_mean", "defburden", "defburden_w_mean", "protest_count", "protest_other", "protest_other_w_mean", "protest_count_w_mean", ends_with("change"), ends_with("growth")),
            list(c_mean = ~mean(., na.rm = TRUE),
                 c_demeaned = ~(.) - mean(., na.rm = TRUE))) %>%
  ungroup() %>% # I want to make sure the standardized demeaned scores, which are done by country, are standardized aacross the entire population of cases. Otherwise massive changes are smushed into the same tiny scale as smaller changes.
  mutate_at(vars("v2x_polyarchy", "v2x_libdem", "pop", "gdp", "troops", "troops_change", "troops_w_mean", "protest_other", "idealdistance_2", "conflict_dummy", "us_war", "us_ally", "defburden_w_mean", "anti_us_protest_w_mean", "exports_from_us", "imports_to_us", ends_with("c_demeaned"), ends_with("c_mean"), ends_with("growth"), ends_with("change")),
            list(z = ~arm::rescale(.),
                 max = ~(.)/max(., na.rm = TRUE))) %>% 
  mutate_at(vars("v2x_polyarchy", "v2x_libdem", "v2x_polyarchy_c_mean", "v2x_polyarchy_c_mean_z", "v2x_polyarchy_c_demeaned_z", "v2x_polyarchy_c_demeaned", "v2x_libdem_c_mean", "v2x_libdem_c_mean_z", "v2x_libdem_c_demeaned_z", "v2x_libdem_c_demeaned", "v2x_polyarchy_z"),
            list(sq = ~(.)^2)) %>% 
  mutate(usmilsize_1k = usmilsize/1000, # This is a really big number for some states. Divide by 1,000,000
         log_usmilsize = log(usmilsize)) %>% 
  group_by(ccode) %>% 
  mutate_at(vars(ends_with("z"), "protest_other", "protest_other_w_mean", "anti_us_protest_w_mean"),
            list(lag = ~dplyr::lag(., order_by = year))) %>% 
  ungroup() %>% 
  mutate(coldwar = if_else(year <= 1989, 1, 0),
         protest_us_dummy = ifelse(anti_us_protest > 0, 1, 0),
         protest_mil_dummy = ifelse(anti_us_mil > 0 , 1, 0),
         region = as.factor(countrycode(ccode, "cown", "region")), # 17 World bank regional groups
         region2 = as.factor(countrycode(ccode, "cown", "continent")), # Five continent regional groups 
         region3 = ifelse(ccode >= 600 & ccode <= 698, "Middle East and North Africa", paste(as.character(region2))),
         region3 = as.factor(region3),
         country = as.factor(country),
         Iraqwar_dummy = ifelse(year == 2003, 1, 0),
         Iraw_dummy = ifelse(ccode == 645, 1, 0),
         mideast_dummy = ifelse(region3 == "Middle East and North Africa", "Middle East and North Africa", "Other Regions"),
         conflictcount = ifelse(is.na(conflictcount), 0, conflictcount),
         conflictcount_low = if_else(is.na(conflictcount_low), 0, conflictcount_low),
         conflictcount_high = if_else(is.na(conflictcount_high), 0, conflictcount_high),
         ccode = ifelse(ccode == 260, 255, ccode)) %>% 
  filter(ccode > 2 & year >= 1988) %>%
  ungroup()


  write_csv(protest.data.final, here::here("Data/Chapter-Protests", "protest-data-final.csv"), append = FALSE)



duplicatecheck <- protest.data.final %>% 
  mutate(dup = 1) %>% 
  group_by(ccode, year) %>% 
  summarise(dups = sum(dup))



# Note: I've performed checks and the standardized variables and regular demeaned variables are all both either positive or negative. We do not see contradictory signs.



```